%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\usepackage{color}

\name{Andrew Xia} % Your name
\address{ \textcolor{blue}{axia-github@mit.edu} \\ \textcolor{blue}{http://qandrew.github.io} \\ \textcolor{blue}{http://github.com/qandrew} } 
\address{Please email for address and phone number}

\begin{document}
%\begin{center}
%I am an aspiring 
%\end{center}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Massachusetts Institute of Technology} \hfill Class of 2017
\\ Candidate for BS in Mathematics and Computer Science (18, 6-2)$\cdot$ GPA: 4.6/5.0 \hfill {\em Cambridge, MA}
\\ {\em Selected Coursework:} 
Applied Discrete Math, Modern Algebra, Real Analysis, Numerical Methods,
Algorithms I, II \& III, Computational Structures, Microcomputer Project Laboratory
%Mechanics, Electromagnetics, Energy in Developing Countries
\\ Awards: HackMIT 2014 Sailthru Prize (Oct 2014)
\\
\\ {\bf Peking University} \hfill Fall 2015
\\ Exchange student, attended classes taught in Chinese  \hfill {\em Beijing, China}
\\
\\ {\bf The Rivers School} \hfill  Class of 2013
\\ Awards: Cum Laude Society, High Honor Roll $\cdot$ GPA: 4.0/4.0 \hfill {\em Weston, MA}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Morgan Stanley {\normalfont $\cdot$ \em Quantitative Finance Intern $\cdot$ New York, NY}}{Summer 2016}{}{}
\item Developed SPG fundamentals page for Securitized Products Group, a web based framework to integrate group's data sources for intuitive cross-desk data comparison and modeling
\item Wrote back end database connections in Q and front end in AngularJS, SCSS and Highcharts API
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Pupil Labs {\normalfont $\cdot$ \em Software Engineering Intern $\cdot$ Berlin, Germany}}{Summer 2015}{}{}
\item Implemented a 3D eye tracking algorithm using ellipse backprojection to help improve pupil detection.
\item Assisted assembly of pupil headsets, helped develop new website. Part of MIT MISTI-Germany Program
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{VISA {\normalfont $\cdot$ \em Software Engineering Intern $\cdot$ San Francisco, CA}}{Summer 2014}{}{}
\item Intern at Visa Labs Incubator division, designed backend for new payments website. 
\item Presented demo of augmented reality payments system to board of directors at end of internship
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{AG Mednet{\normalfont $\cdot$ \em Software Engineering Intern $\cdot$ Boston, MA}}{Summer 2013}{}{}
\item Developed an approximate string matching algorithm in Java that optimized search through company database
\item Decreased search time inside database by 80\% over previous search tool
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Leakage Resistant Public Key Authentication for Embedded Devices{\normalfont $\cdot$ \em Cambridge, MA}}{Sept 2016 - pres.}{}{}
\item {\em Upcoming:} Part of SuperUROP Program in the MIT Energy Efficient Circuits \& Systems Group.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MIT Mixer Series {\normalfont \em $\cdot$ Cambridge, MA}}{Feb 2014 - pres.}{}{}
\item Led, designed and organized the MIT Mixer Series, connecting members of the MIT class of 2017 to meet each other and grab dinner with funding. Runs every semester, over 400 MIT 2017s have signed up and many new friendships formed.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	ACTIVITIES AND LEADERSHIP SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Activities and Leadership}

\begin{list}{$\cdot$}{\leftmargin=0em} % \cdot used for bullets, no indentation
\itemsep -0.5em  % Compress items in list together for aesthetics
\item {\bf MIT Technique} (yearbook club) Living Groups Photo Editor \hfill {\em  2016 - pres.}
%\item {\bf MIT Tour Guide} Also dressed up as \underline{Tim the Beaver}! \hfill {\em 2014 - pres.}
\item {\bf Amphibious Achievement} Director of Program Evaluation, Swim Coach, Academic Mentor \hfill {\em 2013 - pres.} 
\item {\bf Pi Lambda Phi Fraternity} Vice President, Scribe, Community Relations Chair, Historian \hfill {\em 2013 - pres.}
\item {\bf Class Council} 11th Grade Class President \hfill {\em 2011 - 2012}
  
\end{list}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS AND INTERESTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills and Interests}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, Java, HTML/CSS, JavaScript, Matlab, Assembly, C, Q
\\ Human Languages & fluent in English \& Chinese; conversational in German \& Japanese
\\ Interests \& Hobbies & Planespotting, Skiing, Photography, YouTube, Writing, Traveling \& Living Abroad
\\ Favorite Book & The Fountainhead
\end{tabular}

\end{rSection}

%----------------------- End Comments

\end{document}
